\documentclass[12pt]{article}
\usepackage{amsmath, amsthm}
\usepackage{datetime}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{fancyref}
\usepackage{wrapfig}
\usepackage{pifont}
\usepackage{appendix}
\usepackage{caption}
\usepackage{xcolor}
\usepackage[stable]{footmisc}
\usepackage{multicol}

\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}

\usepackage{tikz}
\usepackage{pgf}
\usepgflibrary{fpu}
\usepackage{qtree}
\usetikzlibrary{angles,fit,arrows,calc,math,intersections,through,backgrounds}
\usepackage{pgfplots}
\usepackage{tkz-euclide}

\usepackage{csquotes}
\renewcommand{\mkbegdispquote}[2]{\itshape}

\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage{wasysym}
\usepackage{textcomp}
\usepackage{subfiles}

\title{Working plan 2022}
\date{}
\author{Mingli~Yuan}

\begin{document}

\maketitle
\tableofcontents

\section{The achievement of 2021}

Planning is a sign of success, while the best-laid plans go astray. At the beginning of 2021,  we only have
\begin{itemize}
  \item discrete constructions
  \item flow equations
  \item the conformance of the above two
\end{itemize}

Only a geometry intuition supports us in setting up an idea that we can draw a geometry of arithmetical expressions,
which of cause is not convincing.

But at the end of 2021, when we are writing this document to clarify our current research progress
and give the working schedule for next year to prepare for the new beginning,
we had known that this area might be still neglectable but is a mathematical existence.

We hope we can demonstrate its value at the end of 2022.

\subsection{Basic findings}

From the working log, we can found that Le Zhang gave a new assignments $A$ by separation of variables

\subsection{Main insights}

As a bridge of Geometry, Analysis and Computation.

\section{The plan for 2022}

\subsection{Geometry perspecitve}

minimal-surface-like construction

tube structure

\subsection{Analysis perspecitve}

How an evolving process be described by the tool? An new geometrical view?

A traditional ODE turns into an elastic morphism of the assignments field.

Possible new symbolic rules of difference and integrations?

\subsection{Computation perspecitve}

Combinator space?

\subsection{New synthesis}

the balance of descriptive and compuational complexity?

Chanlenge:

1. Why?
2. Blum theorem

\end{document}
